---
title: "Biomechanics Data"
author: "Riley Feltner"
date: "2023-01-04"
output: html_document
---
#Libraries
```{r}
library(stargazer)
library(dplyr)
library(ggplot2)
library(ggpubr)
```

```{r}
Biomechanics <- read.csv("Pitching Biomechanics Data.csv")
Clean <- na.omit(Biomechanics)
```

```{r}
Biomechanics <- Biomechanics[-c(1)]
```

#Me messing around. Didn't use this in blog--------------------------
#ABSORPTION
#High (>= 75th% lead_knee_absorption_fp_br) vs Low (<= 25th% lead_hip_absorption_fp_br )
```{r}
quantile(Clean$lead_knee_absorption_fp_br, probs = seq(0.33,0.66, 0.33))
#KNEE = 25%: 11.14    50%: 18.70    75%: 26.89
#KNEE = 33%: 13.80    66%: 23.95

quantile(Clean$lead_hip_absorption_fp_br, probs = seq(0.33, 0.66, 0.33))
#HIP =  25%: 70.60    50%: 96.87    75%: 125.55
#HIP =  33%: 81.03    66%: 111.93

#Hip Absorptions       #PROBABLY ADD IN DATA WITH WEIGHT AND FILTER BY THAT FOR THIS SECTION
#Highhip <- filter(Clean, lead_hip_absorption_fp_br >= 111.93) #66th percentile
#mean(Highhip$pitch_speed_mph)

#Lowhip <- filter(Clean, lead_hip_absorption_fp_br <= 81.03) #66th percentile
#mean(Lowhip$pitch_speed_mph)


#Hip and Knee Absorptions
LowKneeHighHip <- filter(Clean, lead_knee_absorption_fp_br <= 13.80 & lead_hip_absorption_fp_br >= 111.93)
mean(LowKneeHighHip$pitch_speed_mph)

HighKneeLowHip <- filter(Clean, lead_knee_absorption_fp_br >= 23.95 & lead_hip_absorption_fp_br <= 81.03)
mean(HighKneeLowHip$pitch_speed_mph)

AboveAverageKneeBelowAverageHip <- filter(Clean, lead_knee_absorption_fp_br >= 18.70 & lead_hip_absorption_fp_br <= 96.87)
mean(AboveAverageKneeBelowAverageHip$pitch_speed_mph)

BelowAverageKneeAboveAverageHip <- filter(Clean, lead_knee_absorption_fp_br <= 18.70 & lead_hip_absorption_fp_br >= 96.87)
mean(BelowAverageKneeAboveAverageHip$pitch_speed_mph)
```

#Correlation of Different Variables on Peak Vertical Ground Reaction Force and Velocity
```{r}
summary(lm(lead_grf_z_max ~ lead_knee_absorption_fp_br, data=Biomechanics))$r.squared
summary(lm(lead_grf_z_max ~ lead_hip_absorption_fp_br, data=Biomechanics))$r.squared
summary(lm(lead_grf_z_max ~ lead_knee_transfer_fp_br, data=Biomechanics))$r.squared
summary(lm(lead_grf_z_max ~ lead_hip_transfer_fp_br, data=Biomechanics))$r.squared
summary(lm(lead_grf_z_max ~ lead_knee_extension_angular_velo_max, data=Biomechanics))$r.squared
summary(lm(lead_grf_z_max ~ lead_knee_extension_from_fp_to_br, data=Biomechanics))$r.squared


summary(lm(pitch_speed_mph ~ lead_knee_absorption_fp_br, data=Biomechanics))$r.squared
summary(lm(pitch_speed_mph ~ lead_hip_absorption_fp_br, data=Biomechanics))$r.squared
summary(lm(pitch_speed_mph ~ lead_knee_transfer_fp_br, data=Biomechanics))$r.squared
summary(lm(pitch_speed_mph ~ lead_hip_transfer_fp_br, data=Biomechanics))$r.squared
summary(lm(pitch_speed_mph ~ lead_knee_extension_angular_velo_max, data=Biomechanics))$r.squared
summary(lm(pitch_speed_mph ~ lead_knee_extension_from_fp_to_br, data=Biomechanics))$r.squared

#Data.frame for Peak Vertical Ground Reaction Force 
PeakVerticalGroundReactionForce <- data.frame("Variable" = c("lead_knee_absorption_fp_br",
                                                             "lead_hip_absorption_fp_br",
                                                             "lead_knee_transfer_fp_br",
                                                             "lead_hip_transfer_fp_br",
                                                             "lead_knee_extension_angular_velo_max", 
                                                             "lead_knee_extension_from_fp_to_br"),
                                              
                                              "Correlation_to_lead_grf_z_max " = c("0.0007",
                                                        "0.0684",
                                                        "0.1260",
                                                        "0.0096",
                                                        "0.0485",
                                                        "0.0127"))

#Data.frame for Velocity
Velocity <- data.frame("Variable" = c("lead_knee_absorption_fp_br",
                                      "lead_hip_absorption_fp_br",
                                      "lead_knee_transfer_fp_br",
                                      "lead_hip_transfer_fp_br",
                                      "lead_knee_extension_angular_velo_max", 
                                      "lead_knee_extension_from_fp_to_br"),
                       
                                      "Correlation_to_velocity " = c("0.0162",
                                                        "0.0360",
                                                        "0.0412",
                                                        "0.0258",
                                                        "0.0130",
                                                        "0.0483"))

```

#plot lead_grf_z_max ~ pitch_speed_mph
```{r}
#Linear
  ggplot(data = Biomechanics, aes(x = lead_grf_z_max, y = pitch_speed_mph)) +
  geom_point(color = "blue")+
  geom_smooth(method = "lm", se=FALSE, color="black", formula = y ~ x) +
  labs(title = "Lead Leg Vertical Ground Reaction Force and Velocity Linear Regression",
       y = "Velocity",
       x = "Lead Leg Vertical Ground Reaction Force",
       caption = "Data: Driveline Baseball | Riley Feltner")+
  theme_minimal()+
  stat_cor(aes(label = ..rr.label..), color = "red", geom = "label", label.y.npc = "top")

#Non Linear
  ggplot(data = Biomechanics, aes(x = lead_grf_z_max, y = pitch_speed_mph)) +
  geom_point(color = "blue")+
  geom_smooth(se = FALSE, color = "black") +
  labs(title = "Lead Leg Vertical Ground Reaction Force and Velocity",
       y = "Velocity",
       x = "Lead Leg Vertical Ground Reaction Force",
       caption = "Data: Driveline Baseball | Riley Feltner")+
  theme_minimal()
```

